\begin{thebibliography}{2}
\label{bibliography}

	\bibitem[Richardson, Amundsen, Ruby 2013]{restapi} L. RICHARDSON, M. AMUNDSEN, S. RUBY: \emph{RESTful Web APIs}. 1st Edition, O’Reilly Media, ISBN 9781449358068 , Kindle Edition, 2013, pp. 406 
   
	\bibitem[Šverma 2015]{sverma} Igor ŠVERMA: \emph{A Component Database Design for the ATLAS Inner Detector at LHC}. Unicorn College s.r.o. 2015, pp. 97  Bachelor’s thesis at Unicorn College at Department  of information  technologies. Supervisor of the Thesis doc. Ing. Václav Vacek, CSc.

	\bibitem[ATLAS ITk website]{atlasitkweb} \emph{Detector description Inner Detector} [online] [quoted 2015-01-02] Available on: <\url{http://www.atlas.ch/inner-detector.html}>

	\bibitem[ATLAS website]{atlasweb} \emph{ATLAS Experiment} [online] [quoted 2015-01-08] Available on: <\url{http://www.atlas.ch/what\_is\_atlas.html}>

	%ToDo tady možná nesedí TDR ISBN
	\bibitem[Atlas TDR 1 1997]{atlas1} ATLAS COLLABORATION: \emph{ATLAS Inner Detector TDR (Technical design report)}, Vol. 1(ISBN 92-9083-102-2) and Vol. 2 (ISBN 92-9083-103-0), CERN/LHCC/97-16, Geneva, 1997, pp. 254
    
	\bibitem[Atlas TDR 2 1997]{atlas2} ATLAS COLLABORATION: \emph{ATLAS Inner Detector TDR(Technical design report), Vol. 2}. Vol. 2 (ISBN 92-9083-103-0), CERN/LHCC/97-16, Geneva, 1997, pp.898
 
	\bibitem[Bie 2015]{apitheory} M. BIEHL: \emph{API Architecture : The Big Picture for Building APIs (API-University Series Book 2)}, ISBN: 150867664X, Kindle Edition, 2015,  pp. 192
	\bibitem[MySQL website]{mysqlweb} \emph{4.2.2 Connecting to the MySQL Server} [online] [quoted 2016-01-04] Available on: <\url{https://dev.mysql.com/doc/refman/5.5/en/connecting.html}>
	
	\bibitem[Robinson 2015]{cambridgeSctPresentation} Dave ROBINSON: \emph{Previous Experience of Databases - The SCT ProducGon Database A (similar) database for ITK} 	[presentation] Prague: ITk Database Workshop, 2015-06-25
	
	\bibitem[McMahon 2015]{databasePresentation} Steve McMAHON: \emph{Production Databases Introduction, requirements, schedule: What, Why, When, Where, Who} 	[presentation] Prague: ITK Database Workshop, 2015-06-25
	
	\bibitem[Gregor,Affolder 2015]{lankfordReviewStrips} Ingrid-Maria GREGOR, Tony AFFOLDER on behalf of the ITK Strip Community: \emph{ITK Strips Status and Plans towards TDR} [presentation] ATLAS Lankford Review, 2015-11-23
	
	\bibitem[Vacek 2015]{vacek} doc. Ing. VACEK, Václav CSc., [ústní sdělení] V Kapslovně 2767/2  Praha, 2015-11-18
	
	\bibitem[Atlas]{atlasExperiment} ATLAS COLLABORATION: \emph{The ATLAS experiment at the CERN Large Hadron Collider}, (ISBN ToDO), pp. 408
	
	\bibitem[GLA website]{glasgowWeb} \emph{ATLAS Semiconductor Tracker (SCT) and Inner Detector (ID)} [online] [quoted 2015-01-08] Available on: <\url{http://www.gla.ac.uk/schools/physics/research/groups/particlephysicsexperiment/researchoverview/detectordevelopment/activities/atlassemiconductortrackersct}>

	\bibitem[CERN Atlas SCT Test website]{cernDaq} \emph{Atlas SCT Test DAQ Online Documentation} [online] [quoted 2015-01-03] Available on: <\url{http://sct-testdaq.home.cern.ch/sct/sctdaq.html}>
	
	\bibitem[CERN Atlas DCS]{cernDcs} \emph{ATLAS  
Detector Control Systems} [online] [quoted 2015-01-03] Available on: <\url{http://atlas.web.cern.ch/Atlas/GROUPS/DAQTRIG/DCS/dcshome.html	}>

	\bibitem[Vacek,Beránek 2015]{presCurrentDatabaseStatus} \emph{ITk Production Database Present Status} [presentation] CERN: ITk Week, 15/09/2015
   
   
\end{thebibliography}

\pagebreak

